---
title: "Playground: Working-Model Comparison"
format:
  html:
    toc: true
    number-sections: true
    code-fold: show
execute:
  warning: false
  message: false
params:
  results_dir: "results/pilot"
---

```{r}
library(dplyr)
library(tidyr)
library(readr)
library(ggplot2)
library(knitr)
library(stringr)

pretty_dist_name <- function(dist) {
  switch(
    dist,
    weibull = "Weibull",
    lognormal = "Log-Normal",
    loglogistic = "Log-Logistic",
    exponential = "Exponential",
    str_to_title(dist)
  )
}

resolve_results_dir <- function(path) {
  candidates <- c(
    path,
    file.path(getwd(), path),
    file.path(dirname(getwd()), path),
    file.path(dirname(dirname(getwd())), path)
  )
  hit <- candidates[dir.exists(candidates)]
  if (length(hit) == 0) stop("Cannot find results_dir: ", path)
  normalizePath(hit[1], winslash = "/", mustWork = TRUE)
}

results_dir <- resolve_results_dir(params$results_dir)
raw_dir <- file.path(results_dir, "raw")
derived_dir <- file.path(results_dir, "derived")
fig_dir <- file.path(results_dir, "figures")
dir.create(fig_dir, recursive = TRUE, showWarnings = FALSE)

run_cfg <- read_csv(file.path(raw_dir, "run_config.csv"), show_col_types = FALSE)
rep_df <- read_csv(file.path(raw_dir, "rep_level_results.csv"), show_col_types = FALSE)
sample_df <- read_csv(file.path(raw_dir, "test_level_samples_rep1_by_tau.csv"), show_col_types = FALSE)
method_tau_summary <- read_csv(file.path(derived_dir, "method_tau_summary.csv"), show_col_types = FALSE)
method_overall_summary <- read_csv(file.path(derived_dir, "method_overall_summary.csv"), show_col_types = FALSE)

target_coverage <- 1 - run_cfg$alpha[1]
wrong_label <- pretty_dist_name(run_cfg$wrong_dist[1])
method_levels <- c(
  "Weibull Plug-in",
  "Cox Plug-in",
  paste0(wrong_label, " Plug-in"),
  "CP + Weibull",
  "CP + Cox",
  paste0("CP + ", wrong_label)
)

method_tau_summary <- method_tau_summary %>%
  filter(method_label %in% method_levels)

sample_df <- sample_df %>%
  filter(method_label %in% method_levels)

method_overall_summary <- method_overall_summary %>%
  filter(method_label %in% method_levels)

method_tau_summary <- method_tau_summary %>%
  mutate(
    method_label = factor(method_label, levels = method_levels),
    estimator_family = factor(estimator_family, levels = c("plug-in", "conformal")),
    working_model = factor(working_model, levels = c("Weibull", "Cox", wrong_label))
  )

sample_df <- sample_df %>%
  mutate(
    method_label = factor(method_label, levels = method_levels),
    covered_label = if_else(covered == 1, "Covered", "Missed"),
    estimator_family = factor(estimator_family, levels = c("plug-in", "conformal")),
    working_model = factor(working_model, levels = c("Weibull", "Cox", wrong_label))
  )

method_color_values <- c(
  "Weibull Plug-in" = "#1b9e77",
  "Cox Plug-in" = "#386cb0",
  "CP + Weibull" = "#1b9e77",
  "CP + Cox" = "#386cb0"
)
method_color_values[paste0(wrong_label, " Plug-in")] <- "#d95f02"
method_color_values[paste0("CP + ", wrong_label)] <- "#d95f02"

method_shape_values <- c(
  "Weibull Plug-in" = 16,
  "Cox Plug-in" = 16,
  "CP + Weibull" = 0,
  "CP + Cox" = 0
)
method_shape_values[paste0(wrong_label, " Plug-in")] <- 16
method_shape_values[paste0("CP + ", wrong_label)] <- 0

plot_nudges <- tibble::tibble(
  method_label = factor(method_levels, levels = method_levels),
  x_nudge = c(-0.015, -0.009, -0.003, 0.003, 0.009, 0.015),
  dx = c(-0.015, 0, 0.015, -0.015, 0, 0.015),
  dy = c(0.0008, 0.0016, 0.0008, -0.0008, -0.0016, -0.0008)
)

save_plot <- function(filename, p, width = 9, height = 5.5, dpi = 300) {
  ggsave(file.path(fig_dir, filename), p, width = width, height = height, dpi = dpi)
  invisible(NULL)
}
```

## Run Metadata

```{r}
kable(run_cfg)
kable(method_overall_summary)
```

Results folder: `r results_dir`

All six methods in this report return predictive intervals of the form $[\widehat L(x), \tau]$.

## Summary Table by Tau

```{r}
summary_table <- method_tau_summary %>%
  transmute(
    tau_quantile = round(tau_quantile, 2),
    method = method_label,
    estimator_family,
    working_model,
    spec_status,
    coverage_mean = round(coverage_mean, 3),
    coverage_ci = sprintf("[%.3f, %.3f]", coverage_ci_low, coverage_ci_high),
    length_mean = round(length_mean, 3),
    length_ci = sprintf("[%.3f, %.3f]", length_ci_low, length_ci_high),
    admin_mass_emp_mean = round(admin_mass_emp_mean, 3)
  ) %>%
  arrange(tau_quantile, method)

kable(summary_table)
```

## Coverage Across Tau

```{r}
p_cov <- ggplot(
  method_tau_summary,
  aes(
    x = tau_quantile,
    y = coverage_mean,
    group = method_label
  )
) +
  geom_hline(yintercept = target_coverage, color = "gray35", linewidth = 0.5) +
  geom_line(linewidth = 0.8) +
  geom_point(
    data = method_tau_summary %>% filter(estimator_family == "plug-in"),
    aes(color = method_label, shape = method_label),
    size = 2.2
  ) +
  geom_point(
    data = method_tau_summary %>% filter(estimator_family == "conformal"),
    aes(color = method_label, shape = method_label),
    size = 2.8,
    stroke = 1.0
  ) +
  geom_errorbar(aes(ymin = coverage_ci_low, ymax = coverage_ci_high), width = 0.015, alpha = 0.85) +
  scale_color_manual(values = method_color_values, breaks = method_levels) +
  scale_shape_manual(values = method_shape_values, breaks = method_levels) +
  scale_x_continuous(breaks = sort(unique(method_tau_summary$tau_quantile))) +
  labs(
    title = "Coverage vs Administrative Horizon",
    x = "tau quantile used in the DGP",
    y = "Mean empirical coverage",
    color = "Method",
    shape = "Method"
  ) +
  theme_bw(base_size = 11)

save_plot("coverage_vs_tau_by_method.png", p_cov, width = 10.5, height = 5.8)
save_plot("coverage_vs_tau_by_method.pdf", p_cov, width = 10.5, height = 5.8)
p_cov
```

## Interval Length Across Tau

```{r}
p_len <- ggplot(
  method_tau_summary,
  aes(
    x = tau_quantile,
    y = length_mean,
    group = method_label
  )
) +
  geom_line(linewidth = 0.8) +
  geom_point(
    data = method_tau_summary %>% filter(estimator_family == "plug-in"),
    aes(color = method_label, shape = method_label),
    size = 2.2
  ) +
  geom_point(
    data = method_tau_summary %>% filter(estimator_family == "conformal"),
    aes(color = method_label, shape = method_label),
    size = 2.8,
    stroke = 1.0
  ) +
  geom_errorbar(aes(ymin = length_ci_low, ymax = length_ci_high), width = 0.015, alpha = 0.85) +
  scale_color_manual(values = method_color_values, breaks = method_levels) +
  scale_shape_manual(values = method_shape_values, breaks = method_levels) +
  scale_x_continuous(breaks = sort(unique(method_tau_summary$tau_quantile))) +
  labs(
    title = "Interval Length vs Administrative Horizon",
    x = "tau quantile used in the DGP",
    y = "Mean interval length",
    color = "Method",
    shape = "Method"
  ) +
  theme_bw(base_size = 11)

save_plot("length_vs_tau_by_method.png", p_len, width = 10.5, height = 5.8)
save_plot("length_vs_tau_by_method.pdf", p_len, width = 10.5, height = 5.8)
p_len
```

## Coverage-Length Tradeoff

```{r}
tradeoff_df <- method_tau_summary %>%
  left_join(plot_nudges, by = "method_label") %>%
  mutate(
    length_plot = length_mean + dx,
    coverage_plot = coverage_mean + dy
  )

p_trade <- ggplot(
  tradeoff_df,
  aes(
    x = length_plot,
    y = coverage_plot,
    color = method_label,
    shape = method_label
  )
) +
  geom_hline(yintercept = target_coverage, color = "gray35", linewidth = 0.5) +
  geom_point(size = 3.0, alpha = 0.72) +
  scale_color_manual(values = method_color_values, breaks = method_levels) +
  scale_shape_manual(values = method_shape_values, breaks = method_levels) +
  facet_wrap(~paste0("tau_q=", formatC(tau_quantile, digits = 2, format = "f")), ncol = 2) +
  labs(
    title = "Coverage-Length Tradeoff by Tau Regime",
    subtitle = "Points are slightly nudged within each tau panel to avoid exact overlap",
    x = "Mean interval length",
    y = "Mean empirical coverage",
    color = "Method",
    shape = "Method"
  ) +
  theme_bw(base_size = 11)

save_plot("coverage_length_tradeoff_by_tau.png", p_trade, width = 11.5, height = 6.8)
save_plot("coverage_length_tradeoff_by_tau.pdf", p_trade, width = 11.5, height = 6.8)
p_trade
```

## Direct Interval Comparison at the Middle Tau

```{r}
focus_tau <- sort(unique(sample_df$tau_quantile))
focus_tau <- if (any(abs(focus_tau - 0.90) < 1e-8)) {
  0.90
} else {
  focus_tau[ceiling(length(focus_tau) / 2)]
}

direct_df <- sample_df %>%
  filter(abs(tau_quantile - focus_tau) < 1e-8)

p_direct <- ggplot(direct_df, aes(y = obs_rank)) +
  geom_segment(aes(x = pi_lower, xend = pi_upper, yend = obs_rank, color = covered_label), alpha = 0.9) +
  geom_point(aes(x = T_star, color = covered_label), size = 1.1) +
  geom_vline(aes(xintercept = tau), color = "gray35", linewidth = 0.45) +
  facet_wrap(~method_label, ncol = 2) +
  scale_color_manual(values = c("Covered" = "#1b9e77", "Missed" = "#d95f02")) +
  labs(
    title = paste0("Rep 1 Direct Interval Comparison at tau Quantile ", formatC(focus_tau, digits = 2, format = "f")),
    subtitle = "Same sampled test units across all plotted methods; common x-axis across panels; rows ordered by true linear predictor x^T beta",
    x = "Time scale",
    y = "Observation rank",
    color = "Coverage"
  ) +
  theme_bw(base_size = 11)

save_plot("interval_examples_focus_tau.png", p_direct, width = 10.5, height = 9)
save_plot("interval_examples_focus_tau.pdf", p_direct, width = 10.5, height = 9)
p_direct
```

## Traceability Notes

Key files in this results folder:

- `raw/run_config.csv`
- `raw/rep_level_results.csv`
- `raw/test_level_samples_rep1_by_tau.csv`
- `derived/method_tau_summary.csv`
- `derived/method_overall_summary.csv`
- `figures/coverage_vs_tau_by_method.pdf`
- `figures/length_vs_tau_by_method.pdf`
- `figures/coverage_length_tradeoff_by_tau.pdf`
- `figures/interval_examples_focus_tau.pdf`
